---
format: typst

execute:
  echo: false
  eval: true

knitr:
  opts_chunk:
    dev: null
---

```{r}
#| label: libraries

library(yaml)
library(glue)
library(purrr)
```

```{r}
#| label: setup

workspace_dir <- Sys.getenv("WORKSPACE_DIR", ".")
meta <- read_yaml(file.path(workspace_dir, "data/meta.yml"))
config <- read_yaml(file.path(workspace_dir, "data/config.yml"))
version_file <- Sys.getenv("CV_VERSION", "versions/full.yml")
version_config <- read_yaml(version_file)
```

```{r}
#| label: preamble
#| output: asis

cat("```{=typst}\n")
cat(
  "#import \"@preview/neat-cv:0.4.0\": contact-info, cv, side, entry,",
  "publications, social-links, item-with-level, item-pills\n"
)
cat("\n\n")

glue(
  "#set text(",
  '  lang: "{config$lang}",',
  '  region: "{config$region}",',
  ")",
  .sep = "\n"
) |>
  cat("\n\n")

positions_str <- glue_collapse(double_quote(meta$positions), ", ")
heading_font_str <- glue_collapse(double_quote(config$heading_font), ", ")
body_font_str <- glue_collapse(double_quote(config$body_font), ", ")

# nolint start: commented_code_linter
glue(
  "#show: cv.with(",
  "  author: (",
  '    firstname: "{meta$firstname}",',
  '    lastname: "{meta$lastname}",',
  "    position: ({positions_str}),",
  '    email: "{meta$email}",',
  "    address: [{meta$address}],",
  '    phone: "{meta$phone}",',
  '    website: "{meta$website}",',
  '    twitter: "{meta$twitter}",',
  '    mastodon: "{meta$mastodon}",',
  '    matrix: "{meta$matrix}",',
  '    github: "{meta$github}",',
  '    gitlab: "{meta$gitlab}",',
  '    linkedin: "{meta$linkedin}",',
  '    researchgate: "{meta$researchgate}",',
  '    scholar: "{meta$scholar}",',
  '    orcid: "{meta$orcid}",',
  #    Custom links require neat-cv v0.6.2
  # '    custom-links: (',
  # '      (',
  # '        icon-name: "car", // Font Awesome icon name',
  # '        label: "DeLorean Time Machine",',
  # '        url: "https://en.wikipedia.org/wiki/DeLorean_time_machine",',
  # '      ),',
  # '      (',
  # '        label: "Back to the Future",',
  # '        url: "https://www.backtothefuture.com/",',
  # '      ),',
  # '    ),',
  "  ),",
  '  profile-picture: image("{meta$profile_picture}"),',
  '  accent-color: rgb("{config$accent_color}"),',
  '  font-color: rgb("{config$font_color}"),',
  '  header-color: rgb("{config$header_color}"),',
  # '  date: "{config$date}",',
  "  heading-font: ({heading_font_str}),",
  "  body-font: ({body_font_str}),",
  "  body-font-size: {config$body_font_size},",
  '  paper-size: "{config$paper_size}",',
  "  side-width: {config$side_width},",
  '  gdpr: {ifelse(config$gdpr, "true", "false")},',
  # '  footer: "{config$footer}",',
  ")",
  .sep = "\n"
) |>
  cat("\n\n")
# nolint end: commented_code_linter

glue(
  "#side[",
  "  = Contact",
  "  #contact-info()",
  "  #v(1fr)",
  "  #social-links()",
  "]",
  .sep = "\n"
) |>
  cat("\n\n")

cat("```\n")
```

```{r}
#| label: sidebar
#| output: asis

sidebar <- read_yaml(file.path(workspace_dir, "data/sidebar.yml"))
if (!is.null(sidebar)) {
  cat("```{=typst}\n")
  cat("#side[\n")
  walk(sidebar, function(section) {
    if (section$type == "new-page") {
      cat("#colbreak()\n\n")
    }

    if (section$type == "align-bottom") {
      cat("#v(1fr)\n\n")
    }

    if (!is.null(section$title)) {
      cat(glue("= {section$title}\n\n"))
    }

    if (section$type == "contact") {
      cat("#contact-info()\n\n")
    }

    if (section$type == "social") {
      cat("#social-links()\n\n")
    }

    if (section$type == "text") {
      cat(glue("{section$content}\n\n"))
    }

    if (section$type == "list") {
      walk(section$items, function(item) {
        glue("- {item}\n\n") |> cat()
      })
    }

    if (section$type == "levels") {
      walk(section$items, function(item) {
        if (!is.null(item$subtitle)) {
          item_str <- glue(
            "#item-with-level(",
            "\"{item$name}\", {item$level},",
            "subtitle: \"{item$subtitle}\"",
            ")"
          )
        } else {
          item_str <- glue(
            "#item-with-level(\"{item$name}\", {item$level})"
          )
        }
        cat(item_str, "\n\n")
      })
    }

    if (section$type == "pills") {
      cat("#item-pills((\n")
      walk(section$items, function(item) {
        glue("  \"{item}\",") |> cat()
      })
      cat("))\n\n")
    }
  })
  cat("]\n")
  cat("```\n")
}
```

```{r}
#| label: load_section

load_section <- function(filename, section_name) {
  entries_spec <- version_config$sections[[section_name]]$entries

  if (is.null(entries_spec) || length(entries_spec) == 0) {
    return(NULL)
  }

  data_path <- file.path(workspace_dir, "data", filename)
  data <- read_yaml(file.path(workspace_dir, "data", filename))

  if (identical(entries_spec, "all")) {
    return(data)
  }

  # Filter and reorder by ID
  filtered_data <- Filter(function(entry) {
    !is.null(entry$id) && entry$id %in% entries_spec
  }, data)

  ordered_data <- list()
  for (id in entries_spec) {
    for (entry in filtered_data) {
      if (!is.null(entry$id) && entry$id == id) {
        ordered_data[[length(ordered_data) + 1]] <- entry
        break
      }
    }
  }

  if (length(ordered_data) == 0) {
    return(NULL)
  }

  ordered_data
}
```

```{r}
#| label: generate_section

generate_section <- function(section_data, section_name, title_field = "title",
                             institution_field = "institution",
                             location_field = "location", date_field = "date",
                             from_field = "from", to_field = "to",
                             desc_field = "details") {
  cat("```{=typst}\n")
  glue("= {section_name}\n\n") |> cat()

  # Get first entry with time period
  prefix_entry <- NULL
  for (i in seq_along(section_data)) {
    if (!is.null(section_data[[i]]$to)) {
      prefix_entry <- section_data[[i]]
      break
    }
  }

  walk(section_data, function(entry) {
    desc <- if (!is.null(entry[[desc_field]])) {
      glue("{trimws(entry[[desc_field]])}")
    } else {
      ""
    }

    if (!is.null(entry[[date_field]])) {
      date <- glue::glue("{entry[[date_field]]}")
    } else if (!is.null(entry[[from_field]])) {
      if (is.null(entry[[to_field]])) {
        date <- glue::glue("{entry[[from_field]]}")
      } else {
        if (identical(entry, prefix_entry)) {
          date <- glue(
            "_From_ {entry[[from_field]]}\n\n_to_ {entry[[to_field]]}"
          )
        } else {
          date <- glue("{entry[[from_field]]}\n\n{entry[[to_field]]}")
        }
      }
    } else {
      date <- NULL
    }

    title <- ifelse(
      is.null(entry[[title_field]]),
      "",
      entry[[title_field]]
    )
    institution <- ifelse(
      is.null(entry[[institution_field]]),
      "",
      entry[[institution_field]]
    )
    location <- ifelse(
      is.null(entry[[location_field]]),
      "",
      entry[[location_field]]
    )
    date <- ifelse(is.null(date), "", date)

    glue::glue(
      "#entry(
        title: [{title}],
        institution: [{institution}],
        location: [{location}],
        date: [{date}],
        [{desc}],
      )"
    ) |>
      cat("\n\n")
  })

  cat("```\n")
}
```

```{r}
#| label: education
#| output: asis

education <- load_section("education.yml", "education")
if (!is.null(education)) {
  generate_section(
    education,
    "Education",
    title_field = "degree",
    institution_field = "institution",
    location_field = "location",
    desc_field = "details"
  )
}
```

```{r}
#| label: experience
#| output: asis

experience <- load_section("experience.yml", "experience")
if (!is.null(experience)) {
  generate_section(
    experience,
    "Experience",
    title_field = "position",
    institution_field = "employer",
    location_field = "location",
    desc_field = "details"
  )
}
```

```{r}
#| label: training
#| output: asis

training <- load_section("training.yml", "training")
if (!is.null(training)) {
  generate_section(
    training,
    "Training",
    title_field = "course",
    institution_field = "trainer",
    location_field = "location",
    desc_field = "details"
  )
}
```

```{r}
#| label: extracurricular
#| output: asis

extracurricular <- load_section("extracurricular.yml", "extracurricular")
if (!is.null(extracurricular)) {
  generate_section(
    extracurricular,
    "Extracurricular Activity",
    title_field = "position",
    institution_field = "organisation",
    location_field = "location",
    desc_field = "details"
  )
}
```

```{r}
#| label: skills
#| output: asis

skills <- load_section("skills.yml", "skills")
if (!is.null(skills)) {
  cat("```{=typst}\n")
  cat("= Skills\n\n")

  walk(skills, function(skill) {
    cat(glue::glue("*{skill$category}:* {skill$items}\n\n"))
  })

  cat("```\n")
}
```

```{r}
#| label: awards
#| output: asis

awards <- load_section("awards.yml", "awards")
if (!is.null(awards)) {
  generate_section(
    awards,
    "Awards",
    title_field = "title",
    institution_field = "issuer",
    location_field = "location",
    date_field = "year",
    desc_field = "description"
  )
}
```

```{r}
#| label: presentations
#| output: asis

presentations <- load_section("presentations.yml", "presentations")
if (!is.null(presentations)) {
  generate_section(
    presentations,
    "Presentations",
    title_field = "type",
    institution_field = "event",
    location_field = "location",
    desc_field = "title"
  )
}
```

```{r}
#| label: software
#| output: asis

software <- load_section("software.yml", "software")
if (!is.null(software)) {
  # Format URLs and add links
  software <- map(software, function(entry) {
    entry$url <- glue::glue(
      "#set text(",
      "features: (\"smcp\": 0)); ",
      "#link(",
      "\"{entry$url}\")",
      "[#text(font: (",
      "\"IBM Plex Mono\", \"Fira Mono\", \"DejaVu Sans Mono\", \"monospace\"",
      "))",
      "[{entry$url}]]"
    )
    entry
  })

  generate_section(
    software,
    "Software",
    title_field = "name",
    institution_field = "url",
    location_field = "repository",
    desc_field = "description"
  )
}
```

```{r}
#| label: publications
#| output: asis

publications_raw_path <- file.path(
  workspace_dir, "data", "sections", "publications.yml"
)
publications <- NULL

if (!is.null(version_config$sections$publications)) {
  publications_raw <- read_yaml(publications_raw_path)

  pub_ids <- version_config$sections$publications$entries
  if (length(pub_ids) == 1 && pub_ids == "all") {
    # Include all publications and remove 'id' field
    publications <- publications_raw
    for (key in names(publications)) {
      publications[[key]]$id <- NULL
    }
  } else {
    # Filter by IDs
    publications <- list()
    for (key in names(publications_raw)) {
      if (
        !is.null(publications_raw[[key]]$id) &&
          publications_raw[[key]]$id %in% pub_ids
      ) {
        publications[[key]] <- publications_raw[[key]]
        # Remove the 'id' field as it's not part of neat-cv format
        publications[[key]]$id <- NULL
      }
    }
    if (length(publications) == 0) publications <- NULL
  }
}

if (!is.null(publications)) {
  cat("```{=typst}\n")
  # Write filtered publications to a temporary YAML file
  temp_pub_file <- "_temp_publications.yml"
  # Make sure author fields are always lists
  for (key in names(publications)) {
    if (
      !is.null(publications[[key]]$author) &&
        is.list(publications[[key]]$author) &&
        length(publications[[key]]$author) == 1
    ) {
      publications[[key]]$author <- list(publications[[key]]$author)
    }
  }
  write_yaml(publications, temp_pub_file, column.major = FALSE)

  cat("= Publications\n\n")

  glue(
    "#publications(
      yaml(\"{temp_pub_file}\"),
      highlight-authors: (\"Brown, Emmett\", \"Brown, Emmett Lathrop\")
    )"
  ) |>
    cat("\n\n")

  cat("#entry([_\\* indicates joint authorship_])\n\n")
  cat("```\n")
}
```
