---
format: typst

execute:
  echo: false
  eval: true

knitr:
  opts_chunk:
    dev: null
---

```{r}
#| label: libraries

suppressPackageStartupMessages({
  library(yaml)
  library(glue)
  library(purrr)
  library(jsonlite)
})
```

```{r}
#| label: setup

workspace_dir <- Sys.getenv("WORKSPACE_DIR", ".")
source(file.path(workspace_dir, "scripts/github-stats.R"))
meta <- read_yaml(file.path(workspace_dir, "data/meta.yml"))
config <- read_yaml(file.path(workspace_dir, "data/config.yml"))
version_file <- Sys.getenv("CV_VERSION", "versions/full.yml")
version_config <- read_yaml(version_file)
```

```{r}
#| label: preamble
#| output: asis

cat("```{=typst}\n")
cat(
  "#import \"@preview/neat-cv:0.7.0\": (",
  "  contact-info, cv, email-link, entry, item-pills, item-with-level,",
  "  publications, side, social-links,",
  ")\n",
  sep = "\n"
)

glue(
  "#set text(",
  '  lang: "{config$lang}",',
  '  region: "{config$region}",',
  ")",
  .sep = "\n"
) |>
  cat("\n\n")

positions_str <- glue_collapse(double_quote(meta$positions), ", ")
heading_font_str <- glue_collapse(double_quote(config$heading_font), ", ")
body_font_str <- glue_collapse(double_quote(config$body_font), ", ")
url_font_str <- glue_collapse(double_quote(config$url_font), ", ")

if (is.null(meta$custom_links) || length(meta$custom_links) == 0) {
  custom_links_str <- ""
} else {
  custom_links_str <- map(
    meta$custom_links, function(link) {
      glue(
        "(\n",
        "  {ifelse(!is.null(link$icon), glue('icon-name: \"{link$icon}\", '), '')}",
        "  label: \"{link$label}\",\n",
        "  url: \"{link$url}\"\n",
        ")"
      )
    }
  ) |> glue_collapse(",\n")
}

# nolint start: commented_code_linter
glue(
  "#show: cv.with(",
  "  author: (",
  '    firstname: "{meta$firstname}",',
  '    lastname: "{meta$lastname}",',
  "    position: ({positions_str}),",
  '    email: "{meta$email}",',
  "    address: [{meta$address}],",
  '    phone: "{meta$phone}",',
  '    website: "{meta$website}",',
  '    twitter: "{meta$twitter}",',
  '    mastodon: "{meta$mastodon}",',
  # '    matrix: "{meta$matrix}",',
  # '    github: "{meta$github}",',
  # '    gitlab: "{meta$gitlab}",',
  '    linkedin: "{meta$linkedin}",',
  # '    researchgate: "{meta$researchgate}",',
  # '    scholar: "{meta$scholar}",',
  # '    orcid: "{meta$orcid}",',
  "    custom-links: (",
  "      {custom_links_str}",
  "    ),",
  "  ),",
  '  profile-picture: image("{meta$profile_picture}"),',
  '  accent-color: rgb("{config$accent_color}"),',
  '  font-color: rgb("{config$font_color}"),',
  '  header-color: rgb("{config$header_color}"),',
  # '  date: "{config$date}",',
  "  heading-font: ({heading_font_str}),",
  "  body-font: ({body_font_str}),",
  "  body-font-size: {config$body_font_size},",
  '  paper-size: "{config$paper_size}",',
  "  side-width: {config$side_width},",
  '  gdpr: {ifelse(config$gdpr, "true", "false")},',
  # '  footer: "{config$footer}",',
  ")",
  .sep = "\n"
) |>
  cat("\n\n")
# nolint end: commented_code_linter

cat("```\n")
```

```{r}
#| label: sidebar
#| output: asis

sidebar <- read_yaml(file.path(workspace_dir, "data/sidebar.yml"))
if (!is.null(sidebar)) {
  cat("```{=typst}\n")
  cat("#side[\n")
  walk(sidebar, function(section) {
    if (section$type == "new-page") {
      cat("  #colbreak()\n\n")
    }

    if (section$type == "align-bottom") {
      cat("  #v(1fr)\n\n")
    }

    if (!is.null(section$title)) {
      glue("  = {section$title}") |> cat("\n")
    }

    if (section$type == "contact") {
      cat("  #contact-info()\n\n")
    }

    if (section$type == "social") {
      cat("  #social-links()\n\n")
    }

    if (section$type == "text") {
      glue("  {section$content}") |> cat("\n\n")
    }

    if (section$type == "list") {
      walk(section$items, function(item) {
        glue("  - {item}") |> cat("\n")
      })
      cat("\n\n")
    }

    if (section$type == "levels") {
      walk(section$items, function(item) {
        if (!is.null(item$subtitle)) {
          item_str <- glue(
            "  #item-with-level(",
            "\"{item$name}\", {item$level},",
            "subtitle: \"{item$subtitle}\"",
            ")"
          )
        } else {
          item_str <- glue(
            "  #item-with-level(\"{item$name}\", {item$level})"
          )
        }
        cat(item_str, "\n")
      })
      cat("\n")
    }

    if (section$type == "pills") {
      cat("  #item-pills((\n")
      walk(section$items, function(item) {
        glue("    \"{item}\",") |> cat("\n")
      })
      cat("  ))\n")
    }
  })

  cat("]\n\n")
  cat("```\n\n")
}
```

```{r}
#| label: load_section_items

load_section_items <- function(filename, entries, url_fields = NULL) {
  if (is.null(entries) || length(entries) == 0) {
    return(NULL)
  }

  data_path <- file.path(workspace_dir, "data", "sections", filename)
  data <- read_yaml(data_path)

  if (identical(entries, "all")) {
    data <- format_urls(data, url_fields)
    return(data)
  }

  # Check all entries exist
  missing_entries <- setdiff(entries, map_chr(data, "id"))
  if (length(missing_entries) > 0) {
    stop(
      glue(
        "The following entries were not found in {filename}: ",
        "{glue_collapse(missing_entries, ', ')}"
      ),
      call. = FALSE
    )
  }

  # Filter and reorder by ID
  filtered_data <- Filter(function(entry) {
    !is.null(entry$id) && entry$id %in% entries
  }, data)

  ordered_data <- list()
  for (id in entries) {
    for (entry in filtered_data) {
      if (!is.null(entry$id) && entry$id == id) {
        ordered_data[[length(ordered_data) + 1]] <- entry
        break
      }
    }
  }

  if (length(ordered_data) == 0) {
    return(NULL)
  }

  format_urls(ordered_data, url_fields)
}
```

```{r}
#| label: format_urls

format_urls <- function(items, url_fields) {
  if (is.null(items) || length(items) == 0 || is.null(url_fields) || length(url_fields) == 0) {
    return(items)
  }

  map(items, function(item) {
    for (field in url_fields) {
      if (!is.null(item[[field]])) {
        item[[field]] <- glue::glue(
          "#set text(",
          "features: (\"smcp\": 0)); ",
          "#link(",
          "\"{item[[field]]}\")",
          "[#text(font: ({url_font_str}))",
          "[{item[[field]]}]]"
        )
      }
    }
    item
  })
}
```

```{r}
#| label: generate_section_content

generate_section_content <- function(section_data, section_name,
                                     title_field = NULL,
                                     institution_field = NULL,
                                     location_field = NULL,
                                     date_field = NULL,
                                     from_field = NULL, to_field = NULL,
                                     desc_field = NULL) {
  title_field <- title_field %||% "title"
  institution_field <- institution_field %||% "institution"
  location_field <- location_field %||% "location"
  date_field <- date_field %||% "date"
  from_field <- from_field %||% "from"
  to_field <- to_field %||% "to"
  desc_field <- desc_field %||% "description"

  cat("```{=typst}\n\n")
  glue("= {section_name}\n\n\n") |> cat()

  # Get first entry with time period
  prefix_entry <- NULL
  for (i in seq_along(section_data)) {
    if (!is.null(section_data[[i]]$to)) {
      prefix_entry <- section_data[[i]]
      break
    }
  }

  walk(section_data, function(entry) {
    desc <- if (!is.null(entry[[desc_field]])) {
      glue("{trimws(entry[[desc_field]])}")
    } else {
      ""
    }

    if (!is.null(entry[[date_field]])) {
      date <- glue::glue("{entry[[date_field]]}")
    } else if (!is.null(entry[[from_field]])) {
      if (is.null(entry[[to_field]])) {
        date <- glue::glue("{entry[[from_field]]}")
      } else {
        if (identical(entry, prefix_entry)) {
          date <- glue(
            "_From_ {entry[[from_field]]}\n\n_to_ {entry[[to_field]]}"
          )
        } else {
          date <- glue("{entry[[from_field]]}\n\n{entry[[to_field]]}")
        }
      }
    } else {
      date <- NULL
    }

    title <- ifelse(
      is.null(entry[[title_field]]),
      "",
      entry[[title_field]]
    )
    institution <- ifelse(
      is.null(entry[[institution_field]]),
      "",
      entry[[institution_field]]
    )
    location <- ifelse(
      is.null(entry[[location_field]]),
      "",
      entry[[location_field]]
    )
    date <- ifelse(is.null(date), "", date)

    glue::glue(
      "#entry(
        title: [{title}],
        institution: [{institution}],
        location: [{location}],
        date: [{date}],
        [{desc}],
      )"
    ) |>
      cat("\n\n")
  })

  cat("```\n")
}
```

```{r}
#| label: generate_publications

generate_publications <- function(section_config) {
  publications_raw_path <- file.path(
    workspace_dir, "data", "sections", section_config$data
  )
  publications <- NULL

  publications_raw <- read_yaml(publications_raw_path)
  pub_ids <- section_config$entries
  if (length(pub_ids) == 1 && pub_ids == "all") {
    # Include all publications and remove 'id' field
    publications <- publications_raw
    for (key in names(publications)) {
      publications[[key]]$id <- NULL
    }
  } else {
    # Check all specified publication IDs exist
    missing_pub_ids <- setdiff(pub_ids, names(publications_raw))
    if (length(missing_pub_ids) > 0) {
      stop(
        glue(
          "The following publication IDs were not found in {section_config$data}: ",
          "{glue_collapse(missing_pub_ids, ', ')}"
        ),
        call. = FALSE
      )
    }

    # Filter by IDs
    publications <- list()
    for (key in names(publications_raw)) {
      if (
        !is.null(publications_raw[[key]]$id) &&
          publications_raw[[key]]$id %in% pub_ids
      ) {
        publications[[key]] <- publications_raw[[key]]
        # Remove the 'id' field as it's not part of neat-cv format
        publications[[key]]$id <- NULL
      }
    }
    if (length(publications) == 0) publications <- NULL
  }

  if (!is.null(publications)) {
    cat("```{=typst}\n\n")
    # Write filtered publications to a temporary YAML file
    temp_pub_file <- "_temp_publications.yml"
    # Make sure author fields are always lists
    for (key in names(publications)) {
      if (
        !is.null(publications[[key]]$author) &&
          is.list(publications[[key]]$author) &&
          length(publications[[key]]$author) == 1
      ) {
        publications[[key]]$author <- list(publications[[key]]$author)
      }
    }
    write_yaml(publications, temp_pub_file, column.major = FALSE)

    glue("= {section_config$name}\n\n\n") |> cat()

    highlight_authors <- section_config$highlight_authors %||% c()
    highlight_authors_str <- glue_collapse(
      double_quote(highlight_authors), ", "
    )
    glue(
      "#publications(
        yaml(\"{temp_pub_file}\"),
        highlight-authors: ({highlight_authors_str})
      )"
    ) |>
      cat("\n\n")

    if (!is.null(section_config$joint_authorship)) {
      glue(
        "#entry([_{section_config$joint_authorship} indicates joint authorship_])\n\n"
      ) |> cat()
    }

    cat("```\n")
  }
}
```

```{r}
#| label: generate_new_page

generate_new_page <- function() {
  cat("```{=typst}\n")
  cat("#colbreak()\n\n")
  cat("```\n\n")
}
```

```{r}
#| label: generate_section

generate_section <- function(section_config) {
  if (!is.null(section_config$type) && section_config$type == "new-page") {
    generate_new_page()
    return(invisible())
  }

  if (is.null(section_config$entries)) {
    stop(
      glue(
        "Section '{section_config$name}' is missing 'entries' field in version config"
      ),
      call. = FALSE
    )
  }

  if (is.null(section_config$data)) {
    stop(
      glue(
        "Section '{section_config$name}' is missing 'data' field in version config"
      ),
      call. = FALSE
    )
  }

  if (!file.exists(file.path(workspace_dir, "data", "sections", section_config$data))) {
    stop(
      glue(
        "Data file '{section_config$data}' for section '{section_config$name}' not found"
      ),
      call. = FALSE
    )
  }

  if (!is.null(section_config$type) && section_config$type == "publications") {
    generate_publications(section_config)
    return(invisible())
  }

  section_data <- load_section_items(
    filename = section_config$data,
    entries = section_config$entries,
    url_fields = section_config$url_fields
  )

  if (is.null(section_data)) {
    return()
  }

  if (isTRUE(section_config$github_stats)) {
    section_data <- add_github_stats( # nolint: object_usage_linter.
      section_data,
      title_field = section_config$title_field %||% "title"
    )
  }

  generate_section_content(
    section_data = section_data,
    section_name = section_config$name,
    title_field = section_config$title_field,
    institution_field = section_config$institution_field,
    location_field = section_config$location_field,
    date_field = section_config$date_field,
    from_field = section_config$from_field,
    to_field = section_config$to_field,
    desc_field = section_config$desc_field
  )
}
```

```{r}
#| label: generate-section-chunks
#| results: hide

sections <- version_config$sections
names(sections) <- map_chr(
  seq_along(sections), \(.i) sections[[.i]]$name %||% paste0("UNNNAMED", .i)
)
src_list <- purrr::map(names(sections), function(.section_name) {
  src <- c(
    "```{r section-<<.section_name>>, results='asis'}",
    "generate_section(sections[['<<.section_name>>']])",
    "```",
    ""
  )

  knitr::knit_expand(text = src, delim = c("<<", ">>"))
})
out <- knitr::knit_child(text = unlist(src_list), options = list(cache = FALSE))
```

`r out`
